---
title: "Week 2 Assignment (LING 609)"
author: "Gabriel Correa"
format: html
---

## R Setup

```{r clean up environment}
rm(list = ls())

```

```{r load libraries}
library(tidyverse)
library(knitr)

```

## Downloading the data

- Paper: Gibson and Wu (2013), "Processing Chinese relative clauses in context"
- Source: https://github.com/vasishth/NicenboimVasishthPart2
  - The column labels do not seem to match the number of columns in the actual data
  - I manually skipped the first row and included an additional column label to match the 10 columns in the data. **However, I don't understand why R says it's seeing 11 columns in the data!**

```{r read .txt from github repo}
path <- "https://raw.githubusercontent.com/vasishth/NicenboimVasishthPart2/refs/heads/master/gibsonwu2012data.txt"
rt.df <- read_table(path, skip=1, col_names = c("id", "subj", "item", "type", "pos", "word", "correct", "rt", "region", "type2"))

```

```{r visualize data}
head(rt.df)
```

## Calculate mean RT and standard error

- The string values are weird!

```{r}
unique(rt.df$type)
unique(rt.df$region)

```

```{r}
mean.RT <- rt.df |>
  filter(region == "\"headnoun\"") |> # filter rows where region = headnoun
  group_by(type) |> # group by RC type
  summarize(mean_rt = mean(rt),
            n = n(),
            standard.error = sd(rt) / sqrt(n))
  
kable(mean.RT)
```

## Summary

- My findings seem to line up with what is reported in Figure 1 of Gibson and Wu (2013).

  - For SRCs, I found a mean RT = 610.5 ms (n = 272, standard error = 46.7).

  - For ORCs, I found a mean RT = 487 ms (n = 275, standard error = 21.1).
